Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
edited lm

## Models 
```{r Linear Regression}
## Create the recipe
rec <- origin %>% 
    recipe(value ~ lat + lon + state) 
rec

model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

wf1 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model)
wf1

res <- fit(wf1, data = train)

## Check performance on the complete training data
res %>% 
    extract_fit_engine() %>% 
    summary()

## Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res <- fit_resamples(wf1, resamples = folds)
res %>% 
    collect_metrics()
```

>>>>

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- origin %>% 
    recipe(value ~ lat + lon + state) 
# rec

# Linear regr. model
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

wf1 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model1)
# wf1

res1 <- fit(wf1, data = train)

# Check performance of lin. regr. model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

# Check  lin. regr. model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```
